Figures

### 2019-04-23 manuscript/figures.Rmd
add stream lulc figure
suppress cafos figure

```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```

>>>>

```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```

```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
```
